---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OddsJamR

<!-- badges: start -->
<!-- badges: end -->

This package lets you interact with the OddsJam.com API. Documentation for the API
is available here: https://developer.oddsjam.com/getting-started/

You will need an API key to use this package. You can get one by emailing api@oddsjam.com

## Installation

You can install the development version of OddsJamR from github.

Use: 

```{r, eval = FALSE}
devtools::install_github("bstrain71/OddsJamR")
```

## Authentication

You must load the library and authenticate with the API using your API key.

```{r auth, eval = FALSE}
library(OddsJamR)
set_OddsJam_api_key("your-key-here")
```

### Core Functions

Get the best lines for a given sport on a given day. Market defaults to Moneyline.

```{r best, eval = FALSE, echo = TRUE}
best <- get_days_best(game_date = '2021-10-07',
                      sport = 'football',
                      market = 'Moneyline')
```

For a list of available markets you will need a gameId - otherwise you will get markets for all games for all sports.

```{r gameId_markets, eval = FALSE, echo = TRUE}
# Get some game IDs
ids <- get_gameIds(sport = 'football',
                   league = 'NFL',
                   startDateAfter = '2021-10-07',
                   startDateBefore = '2021-10-08')

# Look at which games are in the selected date range
ids

# Get the available markets for the first game in the list
markets <- get_markets(gameId = ids$id[1])
```

Once you have a list of markets for a game, you can check the best available lines for that market amongs all available sportsbooks.

```{r best_market, eval = FALSE, echo = TRUE}
best_market <- get_days_best(gameId = ids$id[1],
                             market = markets$name[29])
```

Note that historical odds are not available: you can't get odds for past dates.

Dates must be written in the format 'YYYY-MM-DD' like '2021-10-07'

Sports available are:
-football
-basketball
-baseball
-mma
-boxing
-hockey
-soccer
-tennis
-golf
-motorsports
-esports
