---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OddsJamR

<!-- badges: start -->
<!-- badges: end -->

This package lets you interact with the OddsJam.com API. Documentation for the API
is available here: https://developer.oddsjam.com/getting-started/

You will need an API key to use this package. You can get one by emailing api@oddsjam.com

## Installation

You can install the development version of OddsJamR from github.

Use: 

```{r, eval = FALSE}
devtools::install_github("bstrain71/OddsJamR")
```

## Authentication

You must load the library and authenticate with the API using your API key.

```{r auth, eval = FALSE}
library(OddsJamR)
set_OddsJam_api_key("your-key-here")
```

### Core Functions

Get some game ids for a range of dates. The "game_id" parameter is now required to get odds, so you should start with this function.
```{r get_gameIds, eval = FALSE, echo = TRUE}
ids <- get_gameIds(sport = 'baseball',
                   league = 'MLB',
                   startDateAfter = '2022-08-21',
                   startDateBefore = '2022-08-24')
```

Get a list of leagues. If you leave the <sport> parameter blank you'll get all available leagues for all sports.
```{r get_leagues, eval = FALSE, echo = TRUE}
leagues <- get_leagues(sport = 'football')
```


Get some odds for a given date. Note that the <game_id> parameter is required.

```{r get_odds, eval = FALSE, echo = TRUE}
some_odds <- get_odds(game_id = ids$id[21])
```

Get the best lines for a given game_id.

```{r best, eval = FALSE, echo = TRUE}
best <- get_days_best(game_date = '2022-08-23',
                      sport = 'baseball',
                      game_id = ids$id[21])
```

Note that historical odds are not available: you can't get odds for past dates.

Dates must be written in the format 'YYYY-MM-DD' like '2021-10-07'

Sports available are:
-football
-basketball
-baseball
-mma
-boxing
-hockey
-soccer
-tennis
-golf
-motorsports
-esports
