---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OddsJamR

<!-- badges: start -->
<!-- badges: end -->

This package lets you interact with the OddsJam.com API. Documentation for the API
is available here: https://developer.oddsjam.com/getting-started/

You will need an API key to use this package. You can get one by emailing api@oddsjam.com

## Installation

You can install the development version of OddsJamR from github.

Use: 

``` r
devtools::install_github("bstrain71/OddsJamR")
```

```
## Authentication

You must load the library and authenticate with the API using your API key.


```{r example}
library(OddsJamR)
set_OddsJam_api_key("your-key-here")

```

To get the best sportsbook lines for a given sport on a given day try the code below.

Note that historical odds are not available: you can't get odds for past dates.

Dates must be written in the format 'YYYY-MM-DD' like '2021-10-07'

Sports available are:
-football
-basketball
-baseball
-mma
-boxing
-hockey
-soccer
-tennis
-golf
-motorsports
-esports

```{r best, eval = FALSE, echo = TRUE}
best <- get_days_best(game_date = '2021-10-07',
                      sport = 'football')
```



```{r pressure, echo = FALSE}

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
